Hydra Battles and Cie

### 2021-08-29 doc/hydras.tex
re-reading chapter 2 (partially)
[latex] Prevent line breaks within syntactic units in code
https://github.com/coq-community/hydra-battles/issues/70#issue-980536040

@@

@@

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}

@@

% % \mbox{~}
% % \clearpage
% % \newpage
% % \mbox{~}
% \vspace{10cm}
% \begin{quote} 
% { \Large {\it
% ``I start from one point and go as far as possible.'' }

% John Coltrane.}
% \end{quote}

% \begin{verse}
% Hydra hydra hydram \\

% Hydrae hydrae hydra \\

% Hydrae hydrae hydras \\

% Hydrarum hydris hydris\\
% \end{verse}

@@

@@

Quotations of \coq{} source and answers are progressively replaced from copy-pasted \emph{verbatim} to automatically generated \emph{LaTeX} blocks, using Clément Pit-Claudel's \emph{Alectryon} tool~\cite{alectryonpaper, alectryongithub}.
Many thanks to Jérémy Damour and Théo Zimmermann who designed tools for maintaining consistency between the always evolving \coq{} modules and documentation written in \emph{LaTeX}.

@@

At present, this document is a hybrid version: Chapter~\vref{chapter:hydras} to \vref{chapter:primrec} are fully adapted to \emph{Alectryon}.  The rest of the document (Chapter \vref{chapter-powers} is still to be rewritten.

@@

Alectryon's \emph{LaTeX} mode cannot be mistaken for our hand-made quotations, particularly if you read a color-print.
Here is an example from Chapter~\ref{chapter:primrec}.

@@

Quotations of \coq{} source and answers from Chapter~\ref{chapter-powers}, as well as definitions from Standard Library and
other contributions are displayed as follows.

  \begin{Coqsrc}
 Definition square (n:nat) := n * n.

 Lemma square_double : exists n:nat, n + n = square n.
 Proof.
    exists 2. 
  \end{Coqsrc}

Answers from \coq{} (including subgoals, error messages, etc.) are displayed in slanted style
with a different background color.

 \begin{Coqanswer}
 1 subgoal, subgoal 1 (ID 5)

  ============================
   2 + 2 = square 2

 \end{Coqanswer}

 \begin{Coqsrc}
   reflexivity.
Qed.
 \end{Coqsrc}

>>>>

% Prevent breaks in the middle of syntactic units
\let\OldPY\PY
\def\PY#1#2{\OldPY{#1}{\mbox{#2}}}

@@

%%% \snippets{A,B,C,…} inputs a series of snippets as one block (with \itemsep
%%% between them).  A, B, C should be paths to files in movies/snippets/.
\usepackage{etoolbox}
\makeatletter
\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{movies/snippets/#1}}}
\makeatother

@@

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}

@@

@@

% \mbox{~}
\clearpage
% \newpage
% \mbox{~}
\begin{quote}
 (Aprieta el bast\'on con las dos manos, se yergue un tanto,
casi con entusiasmo) ¡Caramba! Claro... los n\'umeros
transfinitos, Kantor...

[ Jorge Luis Borges]
\end{quote}
\vspace{2cm}
\begin{quote}
  Nessun senso percepisce l'infinito. Nessun senso permette di concludere ch'esso esista. L'infinito, in effetti, non puo' essere l'oggetto dei sensi.

  [Giordano Bruno] \emph{De l'infinito, universo e mondi}
\end{quote}

\vspace{2cm}
\begin{quote} 
I start from one point and go as far as possible.

[John Coltrane]
\end{quote}

@@

Quotations of \coq{} source and answers are progressively replaced from copy-pasted \emph{verbatim} to automatically generated \emph{LaTeX} blocks, using Clément Pit-Claudel's \emph{Alectryon} tool~\cite{alectryonpaper, alectryongithub}.
Many thanks to Jérémy Damour, Clément Pit-Claudel  and Théo Zimmermann who designed tools for maintaining consistency between the always evolving \coq{} modules and documentation written in \emph{LaTeX}.

@@

@@

Here is an example from Chapter~\ref{chapter:primrec}.

@@

Quotations of \coq{} source  from Standard Library and code which lead to compilation error or too long computations are displayed as follows.

\begin{Coqsrc}
Definition fib_eucl gamma `{Hgamma: Strategy gamma} n :=
  let c := make_chain gamma  n
  in let r := chain_apply c (M:=Mul2) (1,0) in
       fst r + snd r.

Compute fib_eucl dicho 153.
\end{Coqsrc}

\begin{Coqanswer}
    = 68330027629092351019822533679447
     : N
\end{Coqanswer}
